---
title: "Statistical Learning, Homework-01"
author: "Barba Paolo, Candi Matteo, Costantini Silvia, Vestini Maria Vittoria"
date: '2023-05-10'



output: 
  html_document:
    code_folding: hide
    theme: 
      color-contrast-warnings: false
      bg: "#2B3E50"
      fg: "#B8BCC2"
      primary: "#EA80FC"
      secondary: "#00DAC6"
      base_font:
      google: Prompt
      heading_font:
        google: Proza Libre
---

```{r setup, include=FALSE}
if (requireNamespace("thematic")) 
  thematic::thematic_rmd(font = "auto")
```

```{r package, message=FALSE}

rm(list = ls())

# Set reproducibility -----------------------------------------------------
seed <- 1234
set.seed(seed) 

# Libraries and Data ---------------------------------------------------------------

pkt <- c('glmnet', 'NMOF', 'parallel', 'snow', 'ggplot2', 'reshape2', 'gridExtra')
invisible(lapply(pkt, require, character.only = TRUE))

```

## Purpose & Statistical tools used

[TODO]

## Be linear in transformed feature space

[TODO]

## Implementation of the truncated power basis

[TODO] Spiegare perchè usiamo solo le potenze dispari

```{r power_function}

# Function used to compute the feature matrix
power_functions <- function(d, q, knots, x){
  X <- matrix(NA, length(x), d+q+1)  # Pre-set the feature matrix 
  for( i in 1:length(x)){            # Loop over the data-points
    
    for( j in 1:(d+q+1) ){           # Loop over the basis used
      
      if ( j <= d+1 ){               # Check if the index belong to the firsts (d+1) indices  
        X[i,j] <- x[i]^(j-1)         # Compute the powers
      }
      
      else                           # The index do not belong to the firsts (d+1) indices  
        if((x[i] - knots[j-(d+1)])^d > 0){      # Check if the power of the difference between the data-point and the knot is positive
          X[i,j] <- (x[i] - knots[j-(d+1)])^d   # Compute the power of the difference
        }
      else                           # the power is not positive
         X[i,j] <- 0                 # Set the value to 0
    }   
  }
  return(X)                         # Return the feature matrix
}

```

[TODO Matteo]

```{r plot truncated power function, fig.showtext = TRUE, fig.height = 7, fig.width = 12, fig.align = "center", message=FALSE, warning=FALSE}

plot_func <- function(d, q){
  knots <- seq(0, 1, length.out = q+2)[2 : (q+1)]
  df <- data.frame(power_functions(d, q, knots, xx))
  n_col <- ncol(df)
  legend_labels <- c()
  for (i in 1:n_col) legend_labels <- c(legend_labels, paste0('g', i, '(x)'))
  colnames(df) <- legend_labels
  df <- cbind('xx' = xx, df)
  df <- melt(df,  id.vars = 'xx')
  
  graph <- ggplot(data=df, aes(x = xx, y = value, color = variable)) + 
    geom_line(linewidth = 1) + 
    ggtitle(paste0('Plot with d = ', d, ' and  q = ', q)) + 
    xlab('x') +
    ylab('y') +
    theme_light() + 
    theme(panel.grid = element_blank(),
          panel.background = element_rect(fill = NA),
          
          title = element_text(colour = "white"),
          
          plot.background = element_rect(fill = NA, colour = "#2B3E50"), 
          plot.title = element_text(size=16),
          
          axis.line = element_line(color = "white"),
          axis.text = element_text(color = "white", size = 10),
          axis.title.y = element_text(angle = 0, vjust = 0.5),
          
          legend.title = element_blank(),
          legend.text = element_text(size = 10, color = 'white'),
          legend.key = element_rect(color = NA, fill = NA),
          legend.key.size = unit(0.6, "cm"),
          legend.background = element_rect(fill = NA))
      
  return(graph)
}

xx <- seq(0, 1, length.out = 1000)

p1 <- plot_func(1, 3)
p2 <- plot_func(3, 3)
p3 <- plot_func(1, 10)
p4 <- plot_func(3, 10)

grid.arrange(p1, p2, p3, p4, ncol=2)

```

## ChatGPT - Power function
[TODOMatteo]  Vogliamo che i codici in questa sezione non vengano nascosti, come si fa? Se non riesci, basta un modo per mostrarlo come html (carino)

**Request:**

" Can you implement a function in r to compute the truncated power basis, with parameters d, q, knots. Where $g_i=x^{i-1}$ if $i\le(d+1)$ else $g_{d+1+j} = \max((x-knots[j])^d, 0)$ for $j \in [1,q]$? "

**Response:**

" Certainly! Here's a function in R that computes the truncated power basis you described:

```{r GPT, class.source = "fold-show"}

truncated_power_basis <- function(x, d, q, knots) {
  
  # Compute the first d+1 basis functions
  basis <- matrix(0, nrow = length(x), ncol = d+1)
  basis[,1] <- 1
  for (i in 2:(d+1)) {
    basis[,i] <- x^(i-1)
  }
  
  # Compute the remaining basis functions using knots
  for (j in 1:q) {
    basis[,d+1+j] <- pmax((x - knots[j])^d, 0)
  }
  
  return(basis)
}
```


This function takes as input the vector x, the integer d, the integer q, and the vector knots. It returns a matrix with length(x) rows and d+1+q columns, where each column represents a basis function.

To use this function, simply call truncated_power_basis(x, d, q, knots) with your desired inputs. For example, if you want to compute the truncated power basis with d=3, q=2, and knots=c(0.5, 1.5) for the vector x=c(0.2, 0.4, 0.6, 0.8, 1.0, 1.2, 1.4), you would call truncated_power_basis(x, 3, 2, c(0.5, 1.5)). "

Let's try it!

```{r GPtest, error=TRUE, class.source = "fold-show"}

d <- 1
q <- 3
knots <- seq(0, 1, length.out=q)
x <- seq(0, 1, length.out=1000)

M <- truncated_power_basis(x, d, q, knots)

```

Ops! Looks like the ChatBot response doesn't work. So we will try and see how much we have tell it in order to obtain a working function, first thing to do is give it the error we got. 

*For this following part the code will not be directly shown.*

**Second message request: **

"It seems like there is an error with your function, if i try to use it I get this error: "Error in `[<-`(`*tmp*`, , d + 1 + j, value = pmax((x - knots[j])^d, 0)): subscript out of bounds". Could you give me the correct implementation?"

**Second response:**

" I apologize for the error in my previous implementation. Here's an updated version of the truncated_power_basis function that should work correctly:

```{r GPtest2, error=TRUE}

truncated_power_basis <- function(x, d, q, knots) {
  # Compute the first d+1 basis functions
  basis <- matrix(0, nrow = length(x), ncol = d+1)
  basis[,1] <- 1
  for (i in 2:(d+1)) {
    basis[,i] <- x^(i-1)
  }
  
  # Compute the remaining basis functions using knots
  if (q > 0) {
    for (j in 1:q) {
      basis[,d+j+1] <- pmax((x - knots[j])^d, 0)
    }
  }
  
  return(basis)
}
```

..." 

Again it doesn't work, so this time we give the ChatBot a hint, since we know that the problem is that there isn't enough allocated space for the matrix, this should have $q+d+1$ columns instead of $d+1$.

**Third message:**

"It doesn't solve it, I think the problem is in the dimension of the matrix."

**Third response:**

"
I apologize for the continued issue. You are correct that there is an issue with the dimension of the matrix. Here is the corrected implementation of the truncated_power_basis function:
```{r GPtest3, error=TRUE}

truncated_power_basis <- function(x, d, q, knots) {
  # Compute the first d+1 basis functions
  basis <- matrix(0, nrow = length(x), ncol = d+1)
  basis[,1] <- 1
  for (i in 2:(d+1)) {
    basis[,i] <- x^(i-1)
  }
  
  # Compute the remaining basis functions using knots
  if (q > 0) {
    for (j in 1:q) {
      basis[,d+j+1] <- pmax((x - knots[j])^(d*(x >= knots[j])), 0)
    }
  }
  
  return(basis)
}
```

..."

At the end since also this implementation doesn't work we decided to tell the ChatBot how to solve the issue

**Forth message:**

"Still not good, shouldn't the matrix have $q+d+1$ columns since we are trying to evaluate $q+d+1$ functions?"

**Forth response:**

"
You are correct. I apologize for the error. The matrix should have $q + d + 1$ columns since we are computing a total of $q + d + 1$ basis functions. Here is the corrected implementation:
```{r GPtest4, error=TRUE}
truncated_power_basis <- function(x, d, q, knots) {
  # Compute the first d+1 basis functions
  basis <- matrix(0, nrow = length(x), ncol = d+1)
  basis[,1] <- 1
  for (i in 2:(d+1)) {
    basis[,i] <- x^(i-1)
  }
  
  # Compute the remaining basis functions using knots
  if (q > 0) {
    for (j in 1:q) {
      basis[,d+j+1] <- pmax((x - knots[j])^(d*(x >= knots[j])), 0)
    }
  }
  
  return(basis)
}

```

..." 

But again even if we straight up told the Bot what's the problem and how to solve it the function is not working! At the end the only thing left to do is just tell it the code it should use.

**Fifth (and final) message:** 
"You are not allocating the memory for the matrix correctly, basis should be defined as "basis <- matrix(0, nrow = length(x), ncol = d+q+1)""

**Fifth response:**

"You are correct again. I apologize for the confusion. Here is the corrected implementation:

```{r GPtest5, error=TRUE, class.source = "fold-show"}
truncated_power_basis <- function(x, d, q, knots) {
  # Compute the first d+1 basis functions
  basis <- matrix(0, nrow = length(x), ncol = d+q+1)
  basis[,1] <- 1
  for (i in 2:(d+1)) {
    basis[,i] <- x^(i-1)
  }
  
  # Compute the remaining basis functions using knots
  if (q > 0) {
    for (j in 1:q) {
      basis[,d+j+1] <- pmax((x - knots[j])^(d*(x >= knots[j])), 0)
    }
  }
  ?pmax
  return(basis)
}
```

To use this corrected function, simply call truncated_power_basis(x, d, q, knots) with your desired inputs. For example, to compute the truncated power basis with d=3, q=2, and knots=c(0.5, 1.5) for the vector x=c(0.2, 0.4, 0.6, 0.8, 1.0, 1.2, 1.4), you would call truncated_power_basis(x, 3, 2, c(0.5, 1.5)). This should return a matrix with 7 columns. "

Finally we obtain a function without errors!

```{r GPtest final, error=TRUE, class.source = "fold-show"}
truncated_power_basis(seq(0,1,length.out=6), 3, 2, c(0.1, 0.5))
```

Sadly though we realize that from the third response on the ChatBot changed a line of code from $basis[,d+j+1] <- pmax((x - knots[j])^d, 0)$ to $basis[,d+j+1] <- pmax((x - knots[j])^{d*(x >= knots[j])}, 0)$ and now the function indeed does gives an output, but it's not the right one.

# TODO Finisci di scrivere evaluation

## Dataset

[TODO]

```{r dataset}

test_set_vero <- read.csv("test.csv")
train_set <- read.csv("train.csv")

```

## Pre-processed

[TODO]

```{r data - preproocessing 1 , warning= FALSE , echo = FALSE , fig.width = 10}

# Outlier Detection
quant <- range(quantile(train_set$y, c(0.25, 0.75)))
Lower <- quant[1] - 1.5*(diff(quant))
Upper <- quant[2] + 1.5*(diff(quant))

train_set <- train_set[(train_set$y > Lower)& (train_set$y < Upper),]

```

## Vanilla Cross Validation

```{r functions VCV}

# Function to estimate the weights
compute_weights <- function(knots , dataset){
  # Number of knots
  n <- length(knots)
  # Add the bounds 
  knots <- c(0, knots, 1)
   # Define the matrix
  xx <- rep(NA, length(dataset$x))
  
   # For each interval bounded by the knots
  for(i in 1:(n+1)){
    # Check if there are at least 2 data points inside the interval
    if(sum(dataset$x >= knots[i] & dataset$x <= knots[i+1])>1){    
      # Compute the conditional variance 
      v  <- var(dataset$y[(dataset$x >= knots[i]) & (dataset$x <= knots[i+1])]) 
      # Set the weight of the data points equal to the inverse of the variance
      xx[dataset$x >= knots[i] & dataset$x <= knots[i+1]] <- 1 / v              
    } 
    # If there is only one data point
    else if(sum(dataset$x >= knots[i] & dataset$x <= knots[i+1]) == 1){  
      # Since we can't compute the variance of a single data point then we use the previously computed variance
      xx[dataset$x >= knots[i] & dataset$x <= knots[i+1]] <- 1/v
    }
  }
  
  return(xx)
}
if(sum(NULL)){
  print('cciao')
}

# Function used for the cross validation
cross_val_func <- function(x){
  d <- x[1]
  q <- x[2]
  k <- x[3]
  a <- x[4]
  l <- x[5] 
  p <- x[6]
  
  # size of the fold
  l_folds <- nrow(train_set) / k 
  score <- rep(NA, k)
  for ( i in 1:k){
    idx <- ((i-1)*l_folds+1): (i*l_folds)
    cv_test <- train_set[idx,]
    cv_train <- train_set[-idx,]
    
    
    knots <- seq(1/q, p, length.out=q)
    
    M_cv_train <- power_functions(d = d, q = q, knots = knots, x = cv_train$x)
    # M_cv_train <- data.frame(M_cv_train , target = cv_train$y)
    
    M_cv_test <-  power_functions(d = d, q = q, knots = knots, x = cv_test$x)

    hat_weights <- compute_weights(knots = knots , cv_train)
    
    cv_model <- glmnet(M_cv_train, 
                       cv_train$y,
                       family = "gaussian", 
                       alpha=a, 
                       lambda=l,
                       weights = hat_weights)
    
    cv_predictions <- predict(cv_model, M_cv_test)
    
    score[i] <- sqrt(mean((cv_test$y-cv_predictions)^2))
    
  }
  return(mean(score))
}
```